SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
more on Section IV

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that protect web applications against attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it design-based} and {\it behavior-based}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.

Both categories involve more than one subcategories.
For every subcategory we provide elements regarding
every dimension we described in
Section~\ref{sec:dimensions}.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@

@@

       	\item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.

@@

    \label{tab:comp2}

@@

@@

       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to

>>>>

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that protect web applications against attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it design-based} and {\it behavior-based}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Both categories involve more than one subcategories.
For every subcategory we provide elements regarding
every dimension described in Section~\ref{sec:dimensions}.

Table~\ref{tab:comp} groups the various subcategories
and for every mechanism provides the following:

\begin{enumerate}
\item The number of citations of the publication(s) where
the mechanism was presented.
\item Quadruples that show the values of true
positives ({\sc tp}), true negatives ({\sc tn}),
false positives ({\sc fp}), and false negatives
({\sc tn}). For every quadruple there is a corresponding
suffix that indicates whether the testbed was based
on: real-world applications known to be vulnerable
(r), synthetic benchmarks (s), both (a).
If no testing has taken place we add a question
mark (?).
\item The computational overhead of the
mechanism as stated in the publication.
\item The attacks that the mechanism detects.
\end{enumerate}

\noindent
{\sc na} (Not Available) means that a requirement is not
mentioned in the paper. {\sc nq} (Not Quantified)
indicates that a requirement is mentioned in the publication
but it is not quantified.

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of: source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark (?),
indicates that the a homepage for the software was included
in the publication but now it is not available.

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates in which step
the mechanisms detect corresponding attacks.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.52]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@

    \label{tab:comp}

@@

       	\item[1] {\sc na} (Not Available) means that a requirement is not mentioned in the paper.

@@

@@

    \label{tab:avail}

@@

       \item[1] The check mark (\tick) indicates that the publication
       includes a homepage where the reader can refer to, to
